---
title: PNT-CAT (beta)
output:
  github_document:
    keep_html: true
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Beta-version of computer adaptive philadelphia naming test

To run, make sure these packages are installed on your local machine:

```{r cars, eval = F}
# not run
install.packages(c("here", "shiny", "tibble", "dplyr", "tidyr", "ggplot2",
                   "shinyWidgets", "htmltools", "keys", "DT", "shinyjs", "catR",
                   "bslib", "bayestestR"))

```

Then run the following:

```{r, eval = F}
# not run
shiny::runGitHub("aphasia-apps/pnt")
```

Or clone the repository and run locally. 

Update 5-24: Now preliminary version is on shinyapps.io: https://rb-cavanaugh.shinyapps.io/pnt-cat/

Update 7-10 Bugs/issues/feature requests have been moved to [issues](https://github.com/rbcavanaugh/pnt/issues).

- Anyone is welcome to submit an issue with a bug/feedback/feature requests. 

Update 8-12-21: Now can be downloaded as a package! (which will address dependencies)

```{r, eval = F}
install.packages("remotes")
remotes::install_github("aphasia-apps/pnt")
```

