---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# PNT-CAT (beta)

<!-- badges: start -->
<!-- badges: end -->

Beta-version of computer adaptive philadelphia naming test

To run, make sure these packages are installed on your local machine:

```{r cars, eval = F}
# not run
install.packages(c("here", "shiny", "tibble", "dplyr", "tidyr",
                   "shinyWidgets", "keys", "DT", "shinyjs", "catR",
                   "bslib", "bayestestR"))

```

Then run the following:

```{r, eval = F}
# not run
shiny::runGitHub("rbcavanaugh/pnt")
```

Or clone the repository and run locally. 

Update 5-24: Now preliminary version is on shinyapps.io: https://rb-cavanaugh.shinyapps.io/pnt-cat/


## To do list

### Validation

- ~~Check if app is choosing the same items as catpuccino~~
- ~~validate final results in app use (bonus if automated)~~
  - QUESTION: How does catpuccino handle ties? Testing is showing occasional inconsistencies in which items are being chosen, but its only in cases where difficulty is the same (e.g. kite: -0.475 and bridge: -0.475). Shouldn't affect final ability estimate right? 
- ~~ensure no bias in slight differences between catR and catpuccino~~

### For short-term use

- ~~Add slides with practice trials~~
  - ~~NOTE: Responses not currently logged. ok?~~
- Add instructions, background info, and other important info
  - just refer to MRRI vs. including info...?
- produce a results plot, norms, and any other information to interpret the results
- ~~click sound~~
- ~~Make it pretty~~
- ~~indicator that response has been logged~~
- ~~Add full PNT~~

### Longer-term

- randomly select one of 2-3 best next options
- create ability to upload previous file to prevent reuse of previously tested words
- Convert to an R package. I started this, but its tricky and things go wrong so I reverted back. right now, there's an r-package branch to be worked on...
- make a "report" that is downloadable

