---
title: PNT-CAT (beta)
output:
  github_document:
    keep_html: true
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



<!-- badges: start -->
<!-- badges: end -->

Beta-version of computer adaptive philadelphia naming test

To run, make sure these packages are installed on your local machine:

```{r cars, eval = F}
# not run
install.packages(c("here", "shiny", "tibble", "dplyr", "tidyr", "ggplot2",
                   "shinyWidgets", "htmltools", "keys", "DT", "shinyjs", "catR",
                   "bslib", "bayestestR"))

```

Then run the following:

```{r, eval = F}
# not run
shiny::runGitHub("rbcavanaugh/pnt")
```

Or clone the repository and run locally. 

Update 5-24: Now preliminary version is on shinyapps.io: https://rb-cavanaugh.shinyapps.io/pnt-cat/


## To do list

**ARE THERE ANY COPYRIGHT CONCERNS WE NEED TO ADDRESS?**

### Validation

- ~~Check if app is choosing the same items as catpuccino~~
- ~~validate final results in app use (bonus if automated)~~
  - QUESTION: How does catpuccino handle ties? Testing is showing occasional inconsistencies in which items are being chosen, but its only in cases where difficulty is the same (e.g. kite: -0.475 and bridge: -0.475). Shouldn't affect final ability estimate right? 
- ~~ensure no bias in slight differences between catR and catpuccino~~
- ~~Redo validation script to adjust for practice slides~~ Looks good!

### For short-term use

- ~~Add slides with practice trials~~
  - ~~NOTE: Responses not currently logged. ok?~~
- Add instructions, background info, and other important info ALEX
  - just refer to MRRI vs. including info...?
- ~~produce a results plot, norms, and any other information to interpret the results~~
  - ~~QUESTION: plot distribution sd = 1.48? Also, harder to get >3 or <3 in ability... OK~~
- ~~click sound~~
- ~~Make it pretty~~
- ~~indicator that response has been logged~~
- ~~Add full PNT~~
  - ~~QUESTION: Add option to randomize full PNT? Done~~
- ~~Add source code~~
- ~~Add ability estimate to full 175 PNT (random and not-random)~~
- Incorporate PNT stop rule? (transform SEM to information?) ALEX
- Plot: what is the bell curve? ALEX

### Small stuff & Bugs:
- Clearer instructions for progressing through slides
- ~~More informative error messages on non-assessment slides~~
- ~~Spacing throughout app. make sure ipad friendly.~~ Tentatively, this looks better...
- ~~Sound not working on shinyapps.io~~
- ~~UI resizing after opening modal.~~

### Current agenda items:

- create ability to upload previous file to prevent reuse of previously tested words.
  - ~~able to upload and don't repeat~~
  - ~~compare performacne between administrations (hidden results tab only visible if fileupload exists?)~~
  - use prior from previous adminstration?
  - ~~download data with all previous administrations for n = 2+i'th upload.~~
  - ~~added option to mute sound~~
  - ~~removed progress bar to avoid shinyWidgets dependency~~
  
### Longer-term:

- Convert to a progressive web app - very easy. see {shiny.pwa}
- randomly select one of 2-3 best next options
- PNT 60 item with harder items after n = 30
- Convert to an R package. I started this, but its tricky and things go wrong so I reverted back. right now, there's an r-package branch to be worked on...
- make a "report" that is downloadable
  - I think this would just be a formulaic summary paragraph at the top, a small table with the main results
  - and either use DT or another method of storing the output CSV in the report

