---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# pnt

<!-- badges: start -->
<!-- badges: end -->

Barebones structure for implementing a CAT naming test using shiny.

To run, make sure these packages are installed on your local machine:

```{r cars, eval = F}
# not run
install.packages(c("here", "shiny", "tibble", "dplyr", "tidyr",
                   "shinyWidgets", "keys", "DT", "shinyjs", "catR"))

```

Then run the following:

```{r, eval = F}
# not run
shiny::runGitHub("rbcavanaugh/pnt")
```

Or clone the repository and run locally. 

## To do list

### Validation

- Check if app is choosing the same items as catpuccino
- validate final results in app use (bonus if automated)
  - QUESTION: How does catpuccino handle ties? Testing is showing occasional inconsistencies in which items are being chosen, but its only in cases where difficulty is the same (e.g. kite: -0.475 and bridge: -0.475). Shouldn't affect final ability estimate right? 
- ensure no bias in slight differences between catR and catpuccino

### For short-term use

- Add slides with practice trials
- Add instructions, background info, and other important info
- Make it pretty
- produce a results plot, norms, and any other information
- make a "report" that is downloadable

### Longer-term

- randomly select one of 2-3 best next options
- create ability to upload previous file to prevent reuse of previously tested words
