---
title: "PNT-CAT REPORT"
output: pdf_document
urlcolor: blue
params:
  name: NA
  notes: NA
  values: NA
  irt_final: NA
  text: NA
header-includes:
    - \usepackage{booktabs}
    - \usepackage{tabu}
    - \usepackage{longtable}
    - \usepackage{float}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
#options(knitr.kable.NA = '-')
shiny::setProgress(0.1)
```

### Summary 

The Philadelphia Naming Test (PNT; Roach et al., 1996)...

### Results

This test was completed by `r params$name` and scored on `r format(params$values$datetime, format="%B %d %Y %R %Z")`. `r params$text`

### Plots

```{r, echo=F, fig.height=3, fig.width=5, warning = F, fig.align='center'}

plot <- get_plot(params$values, params$irt_final, basesize = 10)
shiny::setProgress(0.4)
plot
shiny::setProgress(0.7)

```

### Administration notes 

*If notes were entered prior to scoring, they will appear below*

```{r, echo = F, results = 'asis'}
cat(params$notes)
shiny::setProgress(0.8)
```


### References

Roach (1996)...

### About this report

This report was generated by the pnt-cat shiny web app located at https://aphasia-apps.shinyapps.io/pnt/. This web-app is open source and the source code is located at https://github.com/aphasia-apps/pnt Comments, feedback, and bug-reports can be made on the github page. The app was developed by Robert Cavanaugh, Alexander Swiderski, Gerasimos Fergadiotis, and William Hula.

```{r, echo = F}
shiny::setProgress(0.9)
```

