---
title: "PNT-CAT REPORT"
output: pdf_document
urlcolor: blue
params:
  values: NA
  download_time: NA
  irt_final: NA
  text: NA
header-includes:
    - \usepackage{booktabs}
    - \usepackage{tabu}
    - \usepackage{longtable}
    - \usepackage{float}
    - \usepackage[default]{sourcesanspro}
    - \usepackage[T1]{fontenc}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
#options(knitr.kable.NA = '-')
shiny::setProgress(0.1)
```

### Summary 

The Philadelphia Naming Test (PNT; Roach et al., 1996)...

### Results

This test was downloaded on `r format(params$download_time, format="%B %d %Y %R %Z")`. `r params$values$text`

### Plots

```{r, echo=F, fig.height=3, fig.width=5, warning = F, fig.align='center'}

plot <- get_plot(params$irt_final, basesize = 10)

shiny::setProgress(0.4)
plot
shiny::setProgress(0.8)

```

Red line reflects current estimate. Shaded area reflects uncertainty in current estiate. The average ability for individuals with aphasia is 50, with a standard deviation of 10. The density plot represents the distribution of ability scores in the calibration sample, which includes 296 cases from the Moss Aphasia Psycholinguistic Project Database and XX cases from NIH/NIDCD Award R03DC014556 (PI: Fergadiotis)

### References

Roach (1996)...

### About this report

This report was generated by the pnt-cat shiny web app located at https://aphasia-apps.shinyapps.io/pnt/. This web-app is open source and the source code is located at https://github.com/aphasia-apps/pnt Comments, feedback, and bug-reports can be made on the github page. The app was developed by Robert Cavanaugh, Alexander Swiderski, Gerasimos Fergadiotis, and William Hula.

```{r, echo = F}
shiny::setProgress(0.9)
```

### How to cite

Robert Cavanaugh, Alexander Swiderski, Gerasimos Fergadiotis and William D. Hula (2021). PNT.CAT: TITLE OF THE APPLICATION. R package version 0.0.0.9000.
  https://github.com/aphaisa-apps/pnt