---
title: "pnt: Computer adaptive forms of the Philadelphia Naming Test"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Getting Started: 

Users of this application should first familiarize themselves with the administration and scoring procedures for the PNT (https://mrri.org/philadelphia-naming-test/), with a focus on the rules for determining the first complete attempt and for identifying correct responses. The application uses only dichotomous correct/incorrect scoring, which can be applied online with sufficient accuracy by trained users. However, because the rules for determining the first complete attempt, and, to a lesser extent, correct responses can be challenging to apply in some cases, we recommend audio recording administrations for offline review. 

Also of note, while the standard PNT administration rules allow examinees up to 30 seconds to respond to each item, consistent with Walker and Schwartz (2012), the validation studies for the present PNT-CAT short forms (Fergadiotis et al., 2019; Hula et al., 2020) allowed only 10 seconds.

Users should also review the different versions of the PNT available and their psychometric properties. These can be found in the Article entitled "PNT-Versions" [**above**](https://aphasia-apps.github.io/pnt/articles/articles/PNT-Versions.html). 

Users may also wish to review the principles of item-response theory and computer adaptive testing. 

1. [Fergadiotis, Casilio, Hula, and Swiderski, 2021](https://www.thieme-connect.com/products/ejournals/abstract/10.1055/s-0041-1727252)
2. The four articles available above
3. https://aswiderski.shinyapps.io/IRTapp/ 

## Using the application:

### 1. Online

The app is now online at https://aphasia-apps.shinyapps.io/PNT-CAT/

### 2. Local Installation

The app can be installed locally via `remotes::install_github()`

*Note: It's likely that installing the package will prompt you to update packages on your local machine. This may be necessary if you have much older versions of some packages installed (e.g. the {bslib} package). The number of packages to update is large, as the current app uses quite a few {tidyverse} apps which have a number of dependencies. Please raise an issue in github if there are any issues downloading.*

1. Download the package: 

```{r, eval = F}
install.packages("remotes")
remotes::install_github("aphasia-apps/pnt")
```

2. Run the app using the built in function

```{r, eval = F}
library(pnt)
pnt::run_app()
```

### 3. Remote access to the app

The app can also be accessed via `shiny::runGitHub()`

1. Necessary packages must be installed first: 

```{r, eval = F}
install.packages(c("here", "shiny", "tibble", "dplyr", "tidyr", "ggplot2",
                   "shinyWidgets", "htmltools", "keys", "DT", "shinyjs", "catR",
                   "bslib", "bayestestR"))
```

2. The app can be run straight from Github

```{r, eval = F}
shiny::runGitHub("aphasia-apps/pnt")
```

*Note: If you get any errors about missing a package, install it, restart your session, and try again*

### 4 .Clone the repository

If desired, the repository can be cloned, and run locally:

```
git clone https://github.com/aphasia-apps/pnt.git
```